\LARGE \bf \papertitle

### 2012-09-20 manuscript.tex
Pre-reinstall commit

%
% ICRA 2013 Paper Submission
% created on Sep 5, 2012
%
\def \papertitle{Cooperative Control for Narrow Passage Traversal with a Flapping-Wing Micro Air Vehicle and Lightweight Ground Station}

@@

%----------------------------------------------------------------------------%
\subsection{h$^2$Bird Ornithoper MAV}
%TODO(humphrey)
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.jpg}
\caption{h$^2$Bird Ornithopter MAV}
\label{fig:H2Bird}
\end{figure}

@@

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird_axes.jpg}
\caption{h$^2$Bird Ornithopter with flight control axes}
\label{fig:H2Bird}
\end{figure}

We use simple controllers to actuate the h$^2$Bird's wing beat frequency, tail rotor, and tail elevator, which we designed to actuate thrust, yaw, and pitch respectively. Due to the high pitch angles experienced by the h$^2$Bird, we use a quaternion representation of vehicle attitude to avoid the numerical instabilities of Euler angle representations. Given a reference attitude $q$, we define the error $q_e$ as the rotation required to reach the reference attitude from the measured attitude. We then linearize the error quaternion to produce body axis angular errors. Three independent proportional-integral-derivative controllers commanding the wing thrust, elevator, and tail propeller. We use this independent PID controller architecture for simplicity in tuning and implementation, and because it demonstrates acceptable performance in the absence of a system model.

@@

@@

@@

%----------------------------------------------------------------------------%
\subsection{MAV Internal Control}
%TODO(cameron)

@@

>>>>

%
% ICRA 2013 Paper Submission
% created on Sep 5, 2012
%
\def \papertitle{Cooperative Control for Window Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station}

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
%TODO(humphrey)

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.jpg}
\caption{H$^2$Bird Ornithopter MAV}
\label{fig:h2bird}
\end{figure}

The flying platform used in this experiment is the H$^2$Bird flapping wing MAV. Built around the Silverlit I-Bird RC flyer powertrain and clap-fling wings, the H$^2$Bird has a wingspan of [40?] cm and weighs [14?] grams fully loaded. A tail propeller and servo-controlled tail elevator provide control in the yaw and pitch axes. An onboard electronics package combines a 40 MIPS microprocessor, 6 DOF IMU, 802.15.4 radio, VGA camera, and motor drivers with a 90 mAh lithium polymer battery for autonomous flight. In routine flight, the H$^2$Bird averages [insert speed] m/s ground speed and can operate for approximately [10] minutes.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of cooperative control}
\label{fig:block_diagram}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird_axes.jpg}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}

Rudimentary attitude control for the H$^2$Bird runs on-board. It estimates pose by naively integrating the IMU and depending on PID for control. The simplistic nature of our state estimation and control is due to the stringent resource constraints applied by the platform.

We use simple controllers to actuate the H$^2$Bird's wing beat frequency, tail rotor, and tail elevator, which we designed to actuate thrust, yaw, and pitch respectively.

Due to the high pitch angles experienced by the H$^2$Bird, we use a quaternion representation of vehicle pose to avoid the numerical instabilities of Euler angle representations. This choice of pose representation also lends itself well to remote guidance, as relative body and world coordinate angular displacements can be represented compactly with quaternion multiplication.

Given a reference pose $q$, we define the error $q_e$ as the rotation required to reach the reference pose from the measured pose. We then linearize the error quaternion to produce body axis angular errors as as inputs to the attitude controllers.

Three independent proportional-integral-derivative controllers commanding the wing thrust, elevator, and tail propeller. We use this independent PID controller architecture for simplicity in tuning and implementation, and because it demonstrates acceptable performance in the absence of a system model.

\begin{equation}
\label{quat_error}
q_e = q'\otimes q_r
\end{equation}

\begin{equation}
\label{quat_angle}
\alpha = 2acos(q_{e,w})
\end{equation}

\begin{equation}
\label{quat_linearize}
Q_e = \alpha*q_e/sin(\alpha /2)
\end{equation}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.jpg}
\caption{Frame sequence from particle filter video, showing particles and state estimate}
\label{fig:pf_screencap}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.png}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_sketch}
\end{figure}

@@

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
%TODO(cameron)
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/window_trials.jpg}
\caption{Plot of camera field-of-view and H$^2$Bird minimum turning radius cone, with experimental trials overlayed.}
\label{fig:experiment_cone}
\end{figure}
